%------------------------
% Author : Pejman Samadi
% Github : https://github.com/pejmans21
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItemWithoutTitle}[1]{
	\item\small{
		{\vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-5pt}
}


\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------

\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{{\huge Pejman Samadi}} \vspace{5pt} \\ 
		Email: \href{mailto:pezhmansamadi21@gmail.com}{~~~~pezhmansamadi21@gmail.com}\\
		Portfolio:
		\href{http://pejmans21.github.io}{pejmans21.github.io} & Mobile: +989124220335~~~~~~ \\
		GitHub:
		\href{https://github.com/pejmans21}
		{~~github.com/pejmans21} &
		LinkedIn: \href{https://www.linkedin.com/in/pejman-samadi/}{ in/pejman-samadi}
	\end{tabular*}
	
	%-----------EXPERINCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	\resumeSubheading{DevOps/MLOps Engineer}{Tehran, Iran}
	{AiMedic (Full-time)}{Mar 2022 - Present}
	\resumeItemListStart
	
	\resumeItem{CI/CD}
	{Designed and implemented CI/CD pipelines using \textbf{GitLab-CI} for multiple projects, reducing deployment time by 30\%.}
	\vspace{1pt}
	
	\resumeItem{Infrastructure as a Code}
	{Utilized \textbf{Ansible} for configuration management and automation of infrastructure tasks, resulting in improved efficiency and reliability of the infrastructure.}
	\vspace{1pt}
	
	\resumeItem{Docker}
	{Dockerize Python, AI, Back-End, and Front-End projects.}
	
	\resumeItem{MLOps}
	{Worked closely with data scientists and ML engineers to deploy machine learning models in production using TensorFlow and Docker.}
	\vspace{1pt}
	
	\resumeItem{Labeling}
	{Developing a Python package to handle data pipelines designed for communication with \textbf{XNAT}, a tool for labeling medical data.}
	\vspace{1pt}
	
	\resumeItem{Monitoring}
	{Monitoring service requests, resource usage, and logs using tools such as \textit{Grafana}, \textit{Prometheus}, and \textit{Loki}.}
	\vspace{-10pt}
	
	\resumeItem{Development Platform}
	{Acted as the GitLab administrator for the company, responsible for maintaining and updating the system to ensure optimal performance and functionality.}
	\vspace{1pt}
	
	\resumeItemListEnd

	\vspace{1pt}

	\resumeSubheading
	{ML/MLOps Engineer}{Tehran, Iran}
	{AiMedic (Part-time)}{Nov 2021 -  Mar 2022}
	\resumeItemListStart
	
	\resumeItem{AI developer}
	{Develop an AI model to detect lung in CXR images.}
	\vspace{1pt}
	
	\resumeItem{Back-End developer}
	{Working w/ Back-End Web Development tools like FastAPI \& Flask.}
	
	\resumeItemListEnd
	
	\vspace{1pt}
	
	\resumeSubheading
	{Summer Internship}{Chicago, US}
	{Upkey (Internship)}{Jul 2021 -  Sep 2021}
	\resumeItemListStart
	
	\item Soft Skills
	\vspace{-5pt}
	\item Entrepreneurship 
	\vspace{-5pt}
	\item Digital Marketing
	
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{University of Tehran}{Tehran, Iran}
	{Master of Business Administration - MBA}{Sep 2022 - Present}
	
	\vspace{2pt}
	
	\resumeSubheading
	{Iran University of Science and Technology}{Tehran, Iran}
	{Bachelor of Engineering - Electrical and Electronics Engineering}{Sep 2017 - Sep 2022}
	
	\resumeSubHeadingListEnd
	\vspace{-3pt}

	%-----------SKILS-----------------
	\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, Swift, Bash}
	\resumeSubItem{Frameworks}{~~ TensorFlow, PyTorch, FastAPI, Flask}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Kubernetes, Docker, Git, Gitlab-CI, GitHub Actions, Ansible, SQLite}
	\resumeSubItem{Platforms}{~~~~~~~Linux, MacOS}
	\resumeSubItem{Soft Skills}{~~~~~~~Problem-Solving, Writing, Time Management}
	
	\resumeSubHeadingListEnd
	
	\vspace{-3pt}
	
	%-----------PROJECTS-----------------
	\section{Projects}
	\resumeSubHeadingListStart
	\resumeSubItem{\href{https://github.com/pejmanS21/LS-Fastapi}{LS-Fastapi (Tensorflow, FastAPI, DVC, Docker, Kubernetes)}}
	{An AI model for lung segmentation in CXR images, deploying with FastAPI. $|$ Use DVC for data version control, and dockerizing web-app. $|$ Deploy projects w/ K8s.}	
	
	\resumeSubItem{\href{https://github.com/pejmanS21/FaceRecognition_Django}{FaceRecognition\_Django (PyTorch, Django, Docker)}}
	{A FaceRecognition module written with facenet\_pytorch. $|$ Use Django as the web framework. $|$ Dockerized project.}	
	
	\vspace{2pt}

	\resumeSubHeadingListEnd
	\vspace{-5pt}	

	%-----------CERTIFICATES-----------------	
	\section{Certificates}
	\resumeSubHeadingListStart
	\resumeSubheading
	{\href{https://coursera.org/verify/ZNW9LRTQ3RCK}{Programming Fundamentals in Swift}}{Coursera}
	{Swift Programming $|$ iOS App Development}{}
	\vspace{1pt}

	\resumeSubheading
	{\href{https://coursera.org/verify/3EM2DANDTPFH}{Version Control}}{Coursera}
	{Version Control $|$ Bash (Unix Shell)}{}
	\vspace{1pt}
	
	\resumeSubheading
	{\href{https://courses.cognitiveclass.ai/certificates/ec992440901c40c49b9dab687e5970d7}{Introduction to Containers, Kubernetes, and OpenShift V2}}{Cognitive Class}
	{Kubernetes $|$ OpenShift V2}{}
	\vspace{1pt}
	
	\resumeSubheading
	{\href{https://quera.org/certificate/ICpPDqCP/}{TASK-ORIENTED COURCE IN LINUX}}{Quera}
	{Linux $|$ Bash (Unix Shell)}{}
	\vspace{1pt}
	
	\resumeSubHeadingListEnd
	
\end{document}
